---
title: "Homework 1"
author: Purnima Sharma
date: "9/15/2020"
output: github_document
---

Solutions to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with specified elements.

```{r}
Prob1_df = 
 tibble(
   samp = rnorm(10),
   samp_gt_0 = samp > 0,
   char_vec = c("a", "b", "c", "d", "e", "f" ,"g", "h", "i", "j"),
   factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod",   "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(Prob1_df, samp))
mean(pull(Prob1_df, samp_gt_0))
mean(pull(Prob1_df, char_vec))
mean(pull(Prob1_df, factor_vec))
```

I can take the mean of numbers and logical variables but not character or factor variables.


```{r}
as.numeric(pull(Prob1_df, samp))
as.numeric(pull(Prob1_df, samp_gt_0))
as.numeric(pull(Prob1_df, char_vec))
as.numeric(pull(Prob1_df, factor_vec))
```

Logical variable is converted to binary code of 0 and 1, conversion does not work for character, and factor gets converted. Explains why character has no mean.


converting logical vector to numeric, and multiplying numeric by the result

```{r}
as.numeric(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
```



converting logical vector to factor, and multiplying numeric by the result

```{r}
as.factor(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
```
Not a possible operation.


converting logical to factor, and the result to numeric,  and multiplying numeric by the result

```{r}
as.numeric(as.factor(pull(Prob1_df, samp_gt_0))) * pull(Prob1_df, samp)
```
End problem 1.


## Problem 2


