---
title: "Homework 1"
author: Purnima Sharma
date: "9/15/2020"
output: github_document
---

Solutions to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with specified elements.

```{r}
Prob1_df = 
 tibble(
   samp = rnorm(10),
   samp_gt_0 = samp > 0,
   char_vec = c("a", "b", "c", "d", "e", "f" ,"g", "h", "i", "j"),
   factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod",   "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(Prob1_df, samp))
mean(pull(Prob1_df, samp_gt_0))
mean(pull(Prob1_df, char_vec))
mean(pull(Prob1_df, factor_vec))
```

I can take the mean of numbers and logical variables but not character or factor variables.


```{r}
as.numeric(pull(Prob1_df, samp))
as.numeric(pull(Prob1_df, samp_gt_0))
as.numeric(pull(Prob1_df, char_vec))
as.numeric(pull(Prob1_df, factor_vec))
```

Logical variable is converted to binary code of 0 and 1, conversion does not work for character, and factor gets converted. Explains why character has no mean.


converting logical vector to numeric, and multiplying numeric by the result

```{r}
as.numeric(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
```



converting logical vector to factor, and multiplying numeric by the result

```{r}
as.factor(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
```
Not a possible operation.


converting logical to factor, and the result to numeric,  and multiplying numeric by the result

```{r}
as.numeric(as.factor(pull(Prob1_df, samp_gt_0))) * pull(Prob1_df, samp)
```
End problem 1.


## Problem 2

Create a scatterplot to check behavior of ggplots for variables of different types, using Penguins dataset.
 
 First we load the "penguins" dataset.
 
```{r load data}
data("penguins", package = "palmerpenguins")
```


### Data description

   The dataset consists of information on penguins based on 8 variables. 
   
    ```{r variable names}
names(penguins)

```
   
 1. *Species* is a variable of type `r class(pull(penguins, species))`, with values of `r unique(pull(penguins, species))`.
 2.  *Island* is a variable of type `r class(pull(penguins, island))`, with values of `r unique(pull(penguins, island))`.
 3.  *Bill_length_mm* is a variable of type `r class(pull(penguins, bill_length_mm))`.
 4.  *Bill_depth_mm* is a variable of type `r class(pull(penguins, bill_depth_mm))`.
 5.  *Flipper_length_mm* is a variable of type `r class(pull(penguins, flipper_length_mm))`.
 6.  *Body_mass_g* is a variable of type `r class(pull(penguins, body_mass_g))`.
 7.  *Sex* is a variable of type `r class(pull(penguins, sex))`.
 8. *Year* is a variable of type `r class(pull(penguins, year))`, with values of `r unique(pull(penguins, year))`.
   
    
 The data frame has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
 

The mean flipper length is `r round(mean(pull(na.omit(penguins, flipper_length_mm)), digits = 2))` mm.
 
 
### Data visuals
 
Code chunk for Scatterplot of flipper_length vs bill_length, using the "species" variable.
 
```{r scatterplot}
plot_df = tibble(
   x = pull(penguins, flipper_length_mm),
   y = pull(penguins, bill_length_mm)
)

ggplot(plot_df, aes(x = x, 
                    y = y, 
                    color = pull(penguins, species))) + geom_point() + labs(title = "Scatterplot: flipper length vs bill length", x = "flipper length (mm)", y = "bill length (mm)")

ggsave("HW1_scatterplot.pdf", height = 4, width = 6)  

```
End problem 2. 

 
